A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
More tweaks

\documentclass[letterpaper]{article}
\usepackage[showframe,pass]{geometry}

@@

\begin{figure}[tb]
    \centering\subfiguretopcaptrue
    \subfigure[][After mapping $1$ to $a$] {
      \LabelTables{$\{1a\}$}
                  {$2$ & 0 \\
                   $3$ & 0 \\
                   $4$ & 1 \\
                   $5$ & 1 \\}
                  {$b$ & 1 \\
                   $c$ & 1 \\
                   $d$ & 0 \\
                   $e$ & 1 \\
                   $f$ & 0 \\}
      \label{fig:alg2}
    }

    \subfigure[][After mapping $2$ to $d$] {
      \LabelTables{$\{1a,2d\}$}
                  {$3$ & 01 \\
                   $4$ & 10 \\
                   $5$ & 11 \\}
                  {$b$ & 11 \\
                   $c$ & 11 \\
                   $e$ & 10 \\
                   $f$ & 01 \\}
      \label{fig:alg3}
    }

    \subfigure[][After mapping $3$ to $f$] {
      \LabelTables{$\{1a,2d,3f\}$}
                  {$4$ & 100 \\
                   $5$ & 111 \\}
                  {$b$ & 111 \\
                   $c$ & 111 \\
                   $e$ & 101 \\}
      \label{fig:alg4}
    }

@@

\begin{scope}[start chain=going below,node distance=3mm]
\foreach \i in {2,3}
  \node[class1node,on chain] (f\i) [label=left: \i] {};
\end{scope}

\begin{scope}[yshift=-1.8cm,start chain=going below,node distance=3mm]
\foreach \i in {4,5}
  \node[class2node,on chain] (f\i) [label=left: \i] {};
\end{scope}

\begin{scope}[xshift=2.2cm,start chain=going below,node distance=3mm]
\foreach \i in {d,f}
  \node[class1node,on chain] (s\i) [label=right: \i] {};
\end{scope}

\begin{scope}[xshift=2.2cm,yshift=-1.5cm,start chain=going below,node distance=3mm]
\foreach \i in {b,c,e}
  \node[class2node,on chain] (s\i) [label=right: \i] {};
\end{scope}

>>>>

\documentclass[letterpaper]{article}
\usepackage[pass]{geometry}

@@

\begin{figure}[tb]
    \centering\subfiguretopcaptrue
    \subfigure[][After mapping $1$ to $a$] {
      \LabelTables{$\{1a\}$}
                  {$2$ & $0$ \\
                   $3$ & $0$ \\
                   $4$ & $1$ \\
                   $5$ & $1$ \\}
                  {$b$ & $1$ \\
                   $c$ & $1$ \\
                   $d$ & $0$ \\
                   $e$ & $1$ \\
                   $f$ & $0$ \\}
      \label{fig:alg2}
    }

    \subfigure[][After mapping $2$ to $d$] {
      \LabelTables{$\{1a,2d\}$}
                  {$3$ & $01$ \\
                   $4$ & $10$ \\
                   $5$ & $11$ \\}
                  {$b$ & $11$ \\
                   $c$ & $11$ \\
                   $e$ & $10$ \\
                   $f$ & $01$ \\}
      \label{fig:alg3}
    }

    \subfigure[][After mapping $3$ to $f$] {
      \LabelTables{$\{1a,2d,3f\}$}
                  {$4$ & $100$ \\
                   $5$ & $111$ \\}
                  {$b$ & $111$ \\
                   $c$ & $111$ \\
                   $e$ & $101$ \\}
      \label{fig:alg4}
    }

@@

\begin{scope}[start chain=going below,node distance=3mm]
\foreach \i in {2,3}
  \node[class1node,on chain] (f\i) [label=left: $\i$] {};
\end{scope}

\begin{scope}[yshift=-1.8cm,start chain=going below,node distance=3mm]
\foreach \i in {4,5}
  \node[class2node,on chain] (f\i) [label=left: $\i$] {};
\end{scope}

\begin{scope}[xshift=2.2cm,start chain=going below,node distance=3mm]
\foreach \i in {d,f}
  \node[class1node,on chain] (s\i) [label=right: $\i$] {};
\end{scope}

\begin{scope}[xshift=2.2cm,yshift=-1.5cm,start chain=going below,node distance=3mm]
\foreach \i in {b,c,e}
  \node[class2node,on chain] (s\i) [label=right: $\i$] {};
\end{scope}
